Structured Versus Decorated Cospans

### 2020-11-18 cospans.tex
small changes regarding mon. Groth. stuff

These correspondences further restrict to the case when the Grothendieck category $(X,\otimes)$ is specifically cocartesian monoidal itself. In that case, opfibrations
$(\X,+)\to(\A,+)$ that strictly preserve chosen coproducts and initial object
%, and such that $+$ preserves cocartesian liftings, Christina: this should ALWAYS be the case, by universal properties!
bijectively correspond to pseudofunctors into the 2-category of cocartesian categories; for more details, see \cite[Corollary 4.7]{MV} and the related discussion.

Finally, we can further restrict to the setting of opfibrations that also preserve pushouts, i.e. all finite colimits, which is important for our purposes. The following result is in fact more general since it relates the existence of any class of colimits in the total category of an opfibration to their existence in the fibres; for a more detailed exposition, see \cite[Corollary~4.9]{Hermida1999}.
%as well as Remark~4.11 therein regarding the non-necessary strictness condition. Is this obscuring or clarifying?

>>>>

These 2-equivalences further restrict to the case when the Grothendieck category $(X,\otimes)$ is specifically cocartesian monoidal itself. In that case, opfibrations
$(\X,+)\to(\A,+)$ that strictly preserve chosen coproducts and initial object
%, and such that $+$ preserves cocartesian liftings, Christina: this should ALWAYS be the case, by universal properties!
bijectively correspond to pseudofunctors into the 2-category of cocartesian categories; for more details, see \cite[Corollary 4.7]{MV} and the related discussion.

Finally, we can further restrict to the setting of opfibrations that also preserve pushouts, i.e.\ all finite colimits, which is important for our purposes. The following result is in fact more general since it relates the existence of any class of colimits in the total category of an opfibration to their existence in the fibres; for a more detailed exposition, see \cite[Corollary~4.9]{Hermida1999}.
%as well as Remark~4.11 therein regarding the non-necessary strictness condition. Is this obscuring or clarifying?
